### 2016-02-26 README.Rmd
rename from eml2 to EML

[![Travis-CI Build Status](https://travis-ci.org/cboettig/eml2.svg?branch=master)](https://travis-ci.org/cboettig/eml2)

# eml2

*Note*: `eml2` is work in progress. Please see the Issues tracker in this repository for details about current issues and development milestonds.

@@

`eml2` has not yet been released.  Please install from GitHub after installing the `devtools` package (from CRAN):

```{r eval=FALSE}
devtools::install_github("cboettig/eml2")
```

@@

```{r}
library("eml2")
f <- system.file("xsd/test/eml.xml", package = "eml2")
eml <- read_eml(f)
```

@@

Eventually `eml2` will provide constructor and extract methods to create and extract common metadata sections from convenient R stuctures (e.g. `data.frames` with unit metadata, common R classes like `Person`, `bibtype`).  For now, the only method to access and modify EML is to use the standard S4 subsetting and constructor methods.

@@

### Creating eml2 class definitions

>>>>

[![Travis-CI Build Status](https://travis-ci.org/cboettig/EML.svg?branch=master)](https://travis-ci.org/cboettig/EML)

# EML

*Note*: `EML` is work in progress. Please see the Issues tracker in this repository for details about current issues and development milestonds.

@@

`EML` has not yet been released.  Please install from GitHub after installing the `devtools` package (from CRAN):

```{r eval=FALSE}
devtools::install_github("cboettig/EML")
```

@@

```{r}
library("EML")
f <- system.file("xsd/test/eml.xml", package = "EML")
eml <- read_eml(f)
```

@@

Eventually `EML` will provide constructor and extract methods to create and extract common metadata sections from convenient R stuctures (e.g. `data.frames` with unit metadata, common R classes like `Person`, `bibtype`).  For now, the only method to access and modify EML is to use the standard S4 subsetting and constructor methods.

@@

### Creating EML class definitions
